---
title: "**Vector Overlay in the city of Salzburg**"
author: "Cesar Aybar"
date: "2020-01-04"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    css: "style.css"
---

```{r setup, include=FALSE}
library(googleCloudStorageR)
library(reticulate)
library(leaflet)
library(leafem)
library(raster)
library(stars)
library(sf)
source("functions.R")
```


# What is the overlay analysis?

Overlay analysis permit to merge different layers in a single one. This technique is suitable to identify
the best or most preferred locations for a specific phenomenon. Between problems that could be solved using overlay analysis include:

- Where to site a new childrendarden.
- Which sites are better for solar power plants.
- Estimate the vulnerability to landslides.

# Area of Interest (AOI) an dataset

The AOI is the city of Salzburg, Austria. The dataset was obtained from ArcGIS REST Services Directory, and download using a [Python script](https://raw.githubusercontent.com/csaybar/digitalearth/master/assigments/spatial_analisys/assigment_01/download_AGOnline.py). After download the shapefiles, a spatialite dataset was created with the following tables:

- **Salzburg City**: Linestring which represent the outline of Salzburg city.
- **Districts Salzburg City**: District of Salzburg city.
- **ZGIS_SBG_LULC**: Land use of Salzburg city.
- **ZGIS_SBG_Geology**: Geology of Salzburg city.

```{r echo=FALSE}
mapview::mapviewOptions(fgb = FALSE)
suppressWarnings(
  suppressMessages(
    map_01()
  )
)
```


# Filter the land use table

The first step of the process was to filter the table **ZGIS_SBG_LULC**. For the assignment, I chose the "Industrial, commercial, public, military, and private units" class. See the map below to visualize these areas in Salzburg city.

```{r echo=FALSE}
mapview::mapviewOptions(fgb = FALSE)
suppressWarnings(
  suppressMessages(
    map_02()
  )
)
```

# Intersect the filtered area and the geology dataset

In SpatiaLite the spatial relations between two different tables (geometries) are made by the Dimensionally Extended 9-Intersection (DE-9IM) model. The intersection operation is realized in 
three-levels: **interior**, **boundary**, and	**exterior**, and it is necessary to have at least one point in common.	The map below displays our results after the intersection.


```{r echo=FALSE}
mapview::mapviewOptions(fgb = FALSE)
suppressWarnings(
  suppressMessages(
    map_03()
  )
)
```

# Aggregation by District

Finally, we will aggregate (grouping) the geology into the district table according to the larger area. Since in SpatialLite there is no a tool called 'Summarize Data' like ArcGIS. We use a for (loop), `ST_INTERSECT`,  and `ST_SUMMARY` to obtain a similar tool. The map below show our results.

```{r echo=FALSE}
mapview::mapviewOptions(fgb = FALSE)
suppressWarnings(
  suppressMessages(
    map_04()
  )
)
```