---
title: "Software Development assignment I"
author:
- name: "<b>Name:</b> Cesar Luis Aybar Camacho (s1078735)"
- name: "<b>Program:</b> Erasmus Copernicus Master in Digital Earth"
date: '<b>Date:</b> `r format(Sys.time(), "%d %B, %Y")`'
abstract: |
  This assignment implements the java classes **CircleArea**, **CircleAreaUserInput**, and **Fibonacci** which calculate the area of a circle of 4 units, the area of a circle specified by a user, and prints the Fibonacci series.
  
output:
  bookdown::gitbook:
    includes:
      in_header: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r htmlTemplate, echo=FALSE}
# Create the external file
img <- htmltools::img(src = "https://user-images.githubusercontent.com/16768318/96349562-be6c7700-10b0-11eb-973d-ce55906dcf7e.jpeg", 
               alt = 'logo', 
               width="10%",
               style = 'position:absolute; top:50px; right:1%; padding:10px;z-index:200;')

htmlhead <- paste0('
<script>
document.write(\'<div class="logos">',img,'</div>\')
</script>
')

readr::write_lines(htmlhead, path = "header.html")

```

# Question N° 01

Create an executable class called "CircleArea", which calculates the area of a circle:

  - The radius of the circle is 4 units

I implemented and set the variables **circle_radius** and **circle_area** in the constructor of the class. 
After that, I created a method **CircleArea.print** to display the results.

```{java, eval=FALSE}
/** Executable class to calculate the area of specific circle*/ 
public class CircleArea {
    Double circle_radius;
    Double circle_area;

    // Create the constructor
    public CircleArea(Double radius) {   
        circle_radius = radius;
        circle_area = Math.PI*radius*radius;
    }
    
    // Print results in a pretty way!
    public void print () {              
        System.out.format(
            String.format(
                "The area of the circle is: %.4f units\n",
                 this.circle_area
            )
        );
    }
    
    public static void main(String[] args) {
        CircleArea circle = new CircleArea(4.0);
        circle.print();
    }
}
```

**Results:**

```{r, eval=TRUE, echo=FALSE}
cat("The area of the circle is: 50.2655 units")
```

# Question N° 02

**Create an executable class called _CircleAreaUserInput_ which calculates the area of a circle:**
  
  - The radius of the circle shall be entered by the user
  - BufferedReader, Scanner
  - Exception Handling (readLine() method)
  - String to Integer conversion

I implemented and set the variables **constructor** in the constructor of the class. 
Secondly, I use the **java.util.Scanner** to get user input and RegEx to test if
the information enter for the user is a number. Finally, I created a  method
**CircleAreaUserInput.print** to display the results.

```{java, eval=FALSE}
/** Executable class to calculate the area of any circle*/ 
import java.util.Scanner;

public class CircleAreaUserInput {
    Double circle_area;
    // Create the constructor
    public CircleAreaUserInput() {
        // Scanner is class which permit us get user input
        Scanner scanner_obj = new Scanner(System.in);
        System.out.print("Enter the radius of the circle in meters: ");

        // Read user input
        String  radius_str = scanner_obj.nextLine();
                
        // Is radius_str non-numeric? 
        if (!isNumeric(radius_str)) {
            // Use the "throw" statement to throw an exception
            throw new IllegalArgumentException(
                "The radius enter is not an number!"
            );
        }

        // Is radius negative? 
        Double radius = Double.parseDouble(radius_str); 
        
        if (radius < 0) {
            // Use the "throw" statement to throw an exception            
            throw new IllegalArgumentException(
                "The radius enter is negative!"
            );
        }

        // Calculate the area of the circle        
        circle_area = Math.PI*radius*radius;
    }

    // Evaluate if string is a number with RegEx.
    private static boolean isNumeric(String str) {
        return str.matches("-?\\d+(\\.\\d+)?");  
    }

    public void print() {
        System.out.format(
            String.format(
                "The area of the circle is: %.4f m²\n", 
                this.circle_area
            )
        );
    }

    public static void main(String[] args) {
        CircleAreaUserInput circle_case = new CircleAreaUserInput();
        circle_case.print();
    }
}
```

**Results:**
```{r echo=FALSE}
cat(
  "
  Enter the radius of the circle in meters: 24\n
  The area of the circle is: 1809.5574 m²
  "
)
```

# Question N° 03

**Create an executable class called _Fibonacci_ which prints the Fibonacci sequence:**

  - Fibonacci: the printed number is the sum of the two previous numbers
  - Definition: the first two numbers are 0 and 1
  - Print 20 iterations

This question was solved through recursion and memoization to reach an **O(n)** of time complexity.
I used a map object to memoize the previous runs.

```{java, eval=FALSE}
/** Implementation of Fibonnaci algorithm with memoization and recursion*/ 

import java.util.Map;
import java.util.List;
import java.util.HashMap;
import java.util.ArrayList;
import java.util.Collections;

public class Fibonnaci {
    int init_number;
    int results;
    
    /** Create the constructor of the class */
    public Fibonnaci() {     
        String init_message = "|Welcome to Fibonnaci generator with memoization|";
        int init_message_length = init_message.length();
        String simple_line = String.format("%s", "-".repeat(init_message_length));
        System.out.println(simple_line);
        System.out.println(init_message);
        System.out.println(simple_line);          
    }

    // 2. Create a map object
    // Hint: A map contains key:value pairs. A HashTable is a special table that
    //       doesn't maintain any order.
    private Map<Integer, Integer> memoization = new HashMap<>();
    
    /** Implementation of fibonnaci algorithm with memoization
    * 
    * @param n Integer. Index of interest of the Fibonnaci series
    * @return Specific Fibonnaci serie value.
    * @throws IllegalArgumentException if the {@code n} is negative.
    *
    */
    private int fibonnaci_algorithm(int n) {
        // 3.1 Is the number negative or non-integer? 
        if (n < 0) {         
            // Use the "throw" statement to throw an exception            
            throw new IllegalArgumentException(
                "The number enter is negative!"
            );
        }        

        if (n == 0 || n == 1) {            
            return n;
        }
        
        // 3.2 This query exist in our Map object?
        if (memoization.containsKey(n)) {            
            return memoization.get(n);
        } else {
            // Fibonnaci is easier to solve trough recursion rather than iteration!
            int fibb_number = fibonnaci_algorithm(n - 1) + fibonnaci_algorithm(n - 2);
            // Adding a key:value to our map object (memoize)
            memoization.put(n, fibb_number);
            return fibb_number; 
        }                        
    }
    
    /**  Pretty display of Fibonacci series
    * 
    * @param n Integer. Index of interest of the Fibonnaci series
    * @return Fibonnaci series.        
    *
    */    
    public void run(int n) {        
        List<Integer> fib_serie = new ArrayList<Integer>();
        // 4.1 Run "fibonnaci_algorithm" in a reverse loop to force to use memoization.
        for (int i = n - 1; i >= 0; i--) {        
            fib_serie.add(fibonnaci_algorithm(i));            
        }
        // 4.2 Reverse the order in a list
        Collections.reverse(fib_serie);

        // 4.3 Print results        
        System.out.println(String.format("fibonnaci.run(%s):", n) + fib_serie);
    }

    public static void main(String[] args) {
        Fibonnaci serie = new Fibonnaci();
        serie.run(20);
    }    
}
```

**Results:**

```{r question_02, eval=TRUE, echo=FALSE}
cat("
------------------------------------------------- \n
|Welcome to Fibonnaci generator with memoization| \n
------------------------------------------------- \n
fibonnaci.run(20):[0, 1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144, 233, 377, 610, 987, 1597, 2584, 4181]
")
```
