---
title: "Radar remote sensing assignment"
author:
- name: "<b>Name:</b> Cesar Luis Aybar Camacho"
- name: "<b>Program:</b> Erasmus Copernicus Master in Digital Earth"
- name: "<b>Code:</b> s1078735"
date: '<b>Date:</b> `r format(Sys.time(), "%d %B, %Y")`'
abstract: |
  
  This report shows all the steps involved in pre-processing and analyzing two Sentinel-1 SAR GRD images via [**SNAP**](https://step.esa.int/main/toolboxes/snap/). The SAR images were taken before and after a forest fire in the summer of 2017 in Andalusia, Spain. Our results show that the burned area corresponds better with **VH** temporal ratio values than with **VV**. 
output:
  bookdown::gitbook:
    includes:
      in_header: header.html
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r htmlTemplate, echo=FALSE}
# Create the external file
img <- htmltools::img(src = "https://user-images.githubusercontent.com/16768318/96349562-be6c7700-10b0-11eb-973d-ce55906dcf7e.jpeg", 
               alt = 'logo', 
               width="10%",
               style = 'position:absolute; top:50px; right:1%; padding:10px;z-index:200;')

htmlhead <- paste0('
<script>
document.write(\'<div class="logos">',img,'</div>\')
</script>
')

readr::write_lines(htmlhead, path = "header.html")

```

# Part I - Classifiers



# Part II - Object features for classification

## Question 1
**What becomes obvious if you compare the values for the two objects of the chessboard segmentation?**


## Question 2
**Which features don‘t make that much sense in this case?**

## Question 3
**How many objects were classified as "water"?**

## Question 4
**What is the area of the whole vegetation class (if you select the vegetation class to generate the feature, it will summarize the values from the grouped sub-classes)?**

## Question 5
**What is the meaning of the distance value when you create the feature?**