---
title: "How close are kindergardens and water containers to ÖJAB-Haus Salzburg?"
output:
  flexdashboard::flex_dashboard:
    storyboard: yes
    social: menu
    source: embed
    css: style.css
---

```{r setup, include=FALSE}
library(googleCloudStorageR)
library(reticulate)
library(leaflet)
library(leafem)
library(raster)
library(stars)
library(sf)
source("functions.R")
```



### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
mapview::mapviewOptions(fgb = FALSE)
question_01_01()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
question_01_02()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
question_02_01()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
question_03_01()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
question_03_02()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
question_03_03()
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>
