---
title: "Getting terrain information in Salzburg Catchments"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    css: "style.css"
---

```{r setup, include=FALSE}
library(googleCloudStorageR)
library(reticulate)
library(leaflet)
library(leafem)
library(raster)
library(stars)
library(sf)
source("functions.R")
knitr::opts_chunk$set(echo = FALSE)
```



# **Area of Interest (AOI)**

Our area of interest is located in the southern part of the state of Salzburg close to Schmitten and Viehhofen cities. It is a small catchment of 120 km2 draining to the Saalach river. The elevation data for this assignment was obtained from the product [ALOS World 3D (AW3D30)](http://www.eorc.jaxa.jp/ALOS/en/aw3d30/aw3d30v11_format_e.pdf). In the map below, we display the slope and the stream network and basin delineation according to the official information of the Land Salzburg.

```{r}
mapview::mapviewOptions(fgb = FALSE)
suppressWarnings(
  suppressMessages(
    question_01_01()
  )
)
```

**Mouse over the pixels to obtain the slope value.**

# **Slope distribution** 

Considering the slope classification of [V. Zhuchkova and E. Rakovskaya, 2017](https://www.researchgate.net/figure/Classification-of-slope-by-V-Zhuchkova-and-E-Rakovskaya_tbl1_322622715). On average, this catchment could be classified as **very steep**, presenting the lowest values near to the main river and the highest ones close to the drainage divide.

```{r}
suppressWarnings(
  suppressMessages(
    question_01_02()
  )
)
```

# **How to estimate the curvature? - I**

In simple words, we can define the **curvature** as the second derivative of a surface, or the slope of the slope. In surface water hydrology, the concept of curvature plays an important role to understand where the water drains off. 

A negative value indicates that the surface is upwardly convex at that cell, and flow will be decelerated. A positive profile indicates that the surface is upwardly concave at that cell, and the flow will be accelerated. A value of zero indicates that the surface is linear (See [curvature function ArcGIS](https://desktop.arcgis.com/en/arcmap/10.3/manage-data/raster-and-images/curvature-function.htm)). The map below displays the profile curvature for our study area.

```{r}
suppressWarnings(
  suppressMessages(
    question_02_00()
  )
)
```

**Mouse over the pixels to obtain the profile curvature values.**


# **How to estimate the curvature? - II**

**However**, the curvature is not the only model that explains deformations. Other models like the TPI (Topographic Position Index) given also information about the convex or concave of the terrain. In a TPI model the negative values, represent valleys, canyon, and bottoms, and the positive values ridges and hilltops. To estimate the TPI we need to apply a convolution operator and estimate the difference between the value of a cell and the mean value of its 8 surrounding cells. 

```{r}
suppressWarnings(
  suppressMessages(
    question_02_01()
  )
)
```

**Mouse over the pixels to obtain the TPI values.**

# **Slope according to the altitute**

For analyzing the local behavior of the slope. The entire catchment was divided into smaller units according to 200m elevation stripes.

```{r}
suppressWarnings(
  suppressMessages(
    question_03_01()
  )
)
```

The results show that the slope values are linearly correlated with the elevation until the
1500 m.a.s.l.

```{r}
suppressWarnings(
  suppressMessages(
    question_03_02()
  )
)
```

# **Cellsize importance** 

This example shows how different is the spatial distribution of slope values if it is used a digital elevation model of 120 m instead of 30 m of spatial resolution.

```{r}
suppressWarnings(
  suppressMessages(
    question_03_03()
  )
)
```

As it can notice, a larger cell size generates values closer to the mean.

```{r}
suppressWarnings(
  suppressMessages(
    question_03_04()
  )
)
```

# **Conclusion**

Terrain analysis is the basis of several earth observation projects. **The digital terrain models (DTM)** derived from DEM, show us that in this specific catchment:

  - The slope change according to the altitude until the 1500 m.a.s.l.

  - There is more common to find negative curvature values in the valleys (low altitude areas).

  - And finally, the cell size (from 30 to 120 meters) changes sightly the first and second statistical moments of the distribution of slope values.

