---
title: "UAV assignment"
author:
- name: "<b>Name:</b> Cesar Luis Aybar Camacho"
- name: "<b>Program:</b> Erasmus Copernicus Master in Digital Earth"
- name: "<b>Code:</b> s1078735"
date: '<b>Date:</b> `r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::gitbook:
    includes:
      in_header: header.html
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r htmlTemplate, echo=FALSE}
# Create the external file
img <- htmltools::img(src = "https://user-images.githubusercontent.com/16768318/96349562-be6c7700-10b0-11eb-973d-ce55906dcf7e.jpeg", 
               alt = 'logo', 
               width="10%",
               style = 'position:absolute; top:50px; right:1%; padding:10px;z-index:200;')

htmlhead <- paste0('
<script>
document.write(\'<div class="logos">',img,'</div>\')
</script>
')

readr::write_lines(htmlhead, path = "header.html")

```

# Question N° 01

**Import the aerial images and align them in order to create a sparse point cloud.**

Photos can be added via  Workflow  > Add photos. Once added all the photos, need to be aligned (Workflow > Align photos, see figure N°01).

The **align photos** process output is a point cloud.

# Question N° 02

**Import the GCPs (.txt-file provided) and distribute them according to the GCP-overview. The detailed views of every GCP will help you to find the correct positions (Note: After the GCPs have been assigned to the respective marks, the sparse point cloud must be updated by clicking on "optimize camera"!).**

Once the images are aligned it is necessary to import the GCP points by **import reference** and change the parameters.


The GCP are used to estimate and improve the global accuracy of the images. The process consist in filter photos with a marker and right-clicking on each marker.


The error after placing the GCPs is 0.05m.

# Question N° 03

**Generate a dense point cloud from your correctly referenced data set**

A dense point cloud is a collection of point positioned which permits us generate 3D visualization. To generate a dense point cloud in Agisoft you need to go to: 
**Workflow > Build dense cloud**.

# Question N° 04

**Generate both DEM and Orthmosaic and to export them in GeoTIFF format. Visualize the dataset in a GIS environment and draw conclusions about their positional accuracy (e.g. by comparing it with a base map).**

Digital Elevation Model is raster object which represent elevation data. To create a Digital Elevation Model go to **Workflow > Build DEM**.

A Orthmosaic is a mosaic of orthophotos go to **Workflow > Build Orthomosaic** 


If me compare our results with a basemap we notices that 




