---
title: "Zinc spatial prediction in the Meuse river"
output:
  flexdashboard::flex_dashboard:
    storyboard: yes
    self_contained: false
    css: style.css
---

```{r setup, include=FALSE}
library(sp)
library(sf)
library(gstat)
library(plotly)
library(raster)
library(leaflet)
library(ggplot2)
library(mapview)
library(rasterVis)
library(tidyverse)
source("functions.R")
mapview::mapviewOptions(fgb = FALSE)
```

### Formal introduction to the **meuse dataset** {data-commentary-width=650}

```{r}
meuse <- create_meuse() 
m1 <- mapview(
  x = meuse, 
  zcol = "dist.m",
  layer.name = "distance to the river (m)",
  legend = TRUE,
  cex=10
)
m1@map
```

-------------------------------------------------------------------------

<div class="floro">
**Stein, Belgium** is an agriculture village which have many problems with soil pollution. Due to the situation, the authorities created the **Meuse** dataset that gives information about the top soil heavy metal concentrations (ppm), along with a number of soil and landscape variables. Heavy metal concentrations are bulk sampled from an area of approximately 15 m x 15 m ([Pebesma, 2020](https://cran.r-project.org/web/packages/gstat/vignettes/gstat.pdf)).

**This dataset contains the following columns:**

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-1wig{font-weight:bold;text-align:left;vertical-align:top}
.tg .tg-0lax{text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-0lax"><span style="font-weight:bold">x:</span></th>
    <th class="tg-0lax"><span style="font-weight:400;font-style:normal">x-coordinate (m)</span></th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-0lax"><span style="font-weight:bold">y:</span></td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">y-coordinate (m)</span></td>
  </tr>
  <tr>
    <td class="tg-0lax"><span style="font-weight:bold;font-style:normal">cadmium:</span></td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">topsoil cadmium concentration, ppm</span></td>
  </tr>
  <tr>
    <td class="tg-0lax"><span style="font-weight:bold">copper:</span></td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">topsoil copper concentration, ppm.</span></td>
  </tr>
  <tr>
    <td class="tg-0lax"><span style="font-weight:bold;font-style:normal">lead:</span></td>
    <td class="tg-0lax">topsoil lead concentration, ppm.</td>
  </tr>
  <tr>
    <td class="tg-0lax"><span style="font-weight:bold">zinc:</span></td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">topsoil zinc concentration, ppm.</span></td>
  </tr>
  <tr>
    <td class="tg-1wig">elev:</td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">relative elevation</span></td>
  </tr>
  <tr>
    <td class="tg-1wig">dist:</td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">distance to river Meuse; obtained from the nearest cell in</span></td>
  </tr>
  <tr>
    <td class="tg-1wig"><span style="font-style:normal">om:</span></td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">organic matter, as percentage</span></td>
  </tr>
  <tr>
    <td class="tg-1wig">ffreq:</td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">flooding frequency class</span></td>
  </tr>
  <tr>
    <td class="tg-1wig">dist.m:</td>
    <td class="tg-0lax"><span style="font-weight:400;font-style:normal">distance to river Meuse (metres), as obtained during the field survey</span></td>
  </tr>
</tbody>
</table>

</div>

### Interpolation of **zinc values** I {data-commentary-width=400}

```{r}
results_varg <- fit_variog()
plot(results_varg$exp, results_varg$theo)
```

-------------------------------------------------------------------------

<div class="floro">

For interpolate zinc values we use **ordinary kriging** method. This is a gaussian
approach provides **always** the [best linear unbiased prediction](https://en.wikipedia.org/wiki/Best_linear_unbiased_prediction) for all predictions based on covariance/variogram estimates. 

To use **kriging** two hypothesis must be fulfilled:

1) The first moment of the sample is stationary.

2) The correlation between random variables solely depends on the spatial distance and is independent of their location.

After estimate the mean on different **spatial bootstrap samples** (it is not shown here), we notice that all random variables follow a uniform distribution (first hypothesis). The no trend in the **spatial autocorrelation** (second hypothesis) of zinc values was measure using an empirical/experimental variogram that was fitted to a spherical variogram model (see left image). We notice that the range is stabilized at around 850 meters.
</div>

### Interpolation of **zinc values** II {data-commentary-width=400}

```{r}
zinc_map <- suppressMessages(
  suppressWarnings(
    zinc_kriging()
  )
)
na.color <- "#FFFFFF00"

zinc_map2_sp <- zinc_map %>% rasterToPolygons
names(zinc_map2_sp) <- c("prediction", "variance")
m2 <- suppressWarnings(
  mapview(
    x = zinc_map2_sp,
    zcol = "prediction",
    alpha.regions = 1,
    lwd = 0,
    legend = TRUE, 
    na.color = na.color, 
    layer.name = "prediction"
  )
)

m3 <- suppressWarnings(
  mapview(
    x = zinc_map2_sp,
    zcol = "variance",
    alpha.regions = 1,
    legend = TRUE,
    lwd = 0,
    popup = TRUE,
    na.color = na.color, 
    layer.name = "variance"
  )
)
m4 <- m2 | m3
m4@map %>% leaflet::setView(5.74508, 50.97297, 14)
```


-------------------------------------------------------------------------

<div class="floro">
Using the spherical variogram model, the kriging weights were calculated by deriving minimum variance and substituting the semivariogram function into the kriging equation. The **left map** shows us the kriging prediction results and the local variance error for zinc values.  
</div>

### **Out-of-sample testing** as a technique to measure the models' accuracy {data-commentary-width=400}
 
<img src="https://upload.wikimedia.org/wikipedia/commons/b/b5/K-fold_cross_validation_EN.svg">

-------------------------------------------------------------------------

<div class="floro">
**out-of-sample testing** or **cross-validation** is a statistical method that could be used to estimate the local and global error of spatial models.

For this example we use **5-fold out-of-sample testing** (see left image). In this algorithm, The original sample is randomly partitioned into k equal sized subsamples. Of the k subsamples, a single subsample is retained as the validation data for testing the model, and the remaining k − 1 subsamples are used as training data. The cross-validation process is then repeated k times, with each of the k subsamples used exactly once as the validation data. The k results can then be averaged to produce a single estimation.

The advantage of this method over repeated random sub-sampling (see right image) is that all observations are used for both training and validation and each observation is used for validation exactly once. The **5-fold cross-validation** is used for zinc spatial prediction.
</div>

### **K-fold out-of-sample** for testing zinc spatial prediction {data-commentary-width=400}
 
```{r}
kriging_cv <- zinc_kriging_cv()
valuesx <- abs(kriging_cv$residual)
m5 <- suppressWarnings(
  mapview(
    x = kriging_cv["residual"],
    cex = valuesx*10,
    alpha.regions = 1,
    legend = TRUE, 
    na.color = na.color, 
    layer.name = "residual"
  )
)
m5@map
```


------------------------------------------------------------------------

<div class="floro">
It can be seen that areas near the river present **positive large residuals**, while values in the inner area, at least most of it, present **negative** and close to zero values.

These results show that in future fieldworks, it would be ideal to collect more data from areas **near the river rather than in inner areas** since it would generate a lower global mean error in the spatial prediction.
</div>

### How much influence the **number of points** in the interpolation? {data-commentary-width=400}
 
```{r}
npoints_importance <- zinc_kriging_cv_npoints()

npoints_importance_mean <- npoints_importance[1]
npoints_importance_mean$mean_exp <- apply(npoints_importance[-1], 1, mean)

colnames(npoints_importance) <- c("npoints", sprintf("experiment_%03d",1:100))
npoints_importance_melt <- npoints_importance %>% 
  pivot_longer(!npoints, names_to = "experiments", values_to = "values")

gg1 <- ggplot(npoints_importance_melt) +
  geom_point(aes(x=npoints, y=values, group = experiments), cex=1,alpha=0.3)+
  geom_line(data = npoints_importance_mean, aes(x = npoints, y = mean_exp), cex = 1) + 
  geom_point(data = npoints_importance_mean, aes(x = npoints, y = mean_exp), cex = 3) + 
  xlab("Number of points") +
  ylab("RMSE") +
  theme_bw()
ggplotly(gg1)
```


-------------------------------------------------------------------------
<div class="floro">
If we random sampling with no replacement the **meuse dataset** and also considering different samples groups **(25, 50, 75, 100, 122, and 155)**. We could indirectly measure the global spatial variance of our experiment. The left image shows the global interpolation error in the y-axis ([RMSE](https://en.wikipedia.org/wiki/Root-mean-square_deviation)) and different samples in x-axis. 

To improve the stability and accuracy of our results, we use **bootstrap aggregating** (running 100 times the same experiment for each random sampling). The results reveal that the less number of points, the higher **RMSE and lower stability**.
</div>

### How much influence the adjust of the variogram in the interpolation? {data-commentary-width=400}

 
```{r}
levelplot(zinc_dranges(), par.settings = viridisTheme)
```

-------------------------------------------------------------------------

<div class="floro">
One of the most important points to create a good spatial prediction model is determine the **spatial dependence** rule. In Inverse Distance Weighting **(IDW)**, the power value is the most important parameter which have to be measured (e.g. with cross-validation). On the other hand, in **ordinary kriging**, we need to adjust the variogram and to be more specific the **range**, which is the maximum distance up to which the spatial autocorrelation exists.

In this experiment we run **kriging ordinary**, with different range values (200, 400, 600, 800, 1000 and 1200). The results illustrates that low range values generate a bull eye effect on the results while larger range values generate smoothed regions.
</div>


### **Conclusion** {data-commentary-width=400}

```{r}
m4@map %>% leaflet::setView(5.74508, 50.97297, 14)
```

-------------------------------------------------------------------------

<div class="floro">
After analyzing the variogram, it can be noticed that zinc values present a clear **spatial autocorrelation**. In addition, the **5-fold cross-validation** shows us that the global error of the spatial model proposed here ($RMSE_{global}$ ) was 0.26 and this value could exponentially increase if the number of points is reduced. 

These results can help decision-makers to design future fieldworks taking 
into account the error map (**prior probability**) generated in this report.
</div>
