---
title: "Geovisualization and Advanced Cartography"
author:
- name: "<b>Name:</b> Cesar Luis Aybar Camacho"
- name: "<b>Program:</b> Erasmus Copernicus Master in Digital Earth"
- name: "<b>Code:</b> s1078735"
date: '<b>Date:</b> `r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::gitbook:
    includes:
      in_header: header.html
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r htmlTemplate, echo=FALSE, warning=FALSE}
# Create the external file
img <- htmltools::img(src = "https://user-images.githubusercontent.com/16768318/96349562-be6c7700-10b0-11eb-973d-ce55906dcf7e.jpeg", 
               alt = 'logo', 
               width="10%",
               style = 'position:absolute; top:50px; right:1%; padding:10px;z-index:200;')

htmlhead <- paste0('
<script>
document.write(\'<div class="logos">',img,'</div>\')
</script>
')

readr::write_lines(htmlhead, path = "header.html")
```

# Assignment 2: Data Exploration and Geovisualization

**Topic: ** Assignment 2 deals with the exploration of interactive tools to explore data through the preparation of different views on the data. 

**Tools:** Tableau (Public)

**Data:**

    • BLUEbikes trip data
    • https://www.bluebikes.com/system-data 
    • https://s3.amazonaws.com/hubway-data/index.html

**Support material:**

    • Overview on visualizations (paper): a tour through the visualization zoo
    • Online help of Tableau
    • …

**Expected outcomes:**

    • Specify three questions about the information contained in the data that you would like to answer
    • Prepare visualizations/diagrams/maps that support answering the questions
    • Prepare a documentation of your questions, visualizations and answers found
    • Take notes about your observations on the strength and weaknesses of the software program 
    • Present the visualization prepared in lesson 10


# Preprocessing.



# Question #1: What is the most recurrent trip?



# Question #2: How much has **BLUEbikes** grown?


1. Create a Dockerfile (expose the port, see below), and run: 

# Question #3: What are the most popular destinations?

1. Create a Dockerfile (expose the port, see below), and run: 
