---
title: "How close are kindergardens and water containers to ÖJAB-Haus Salzburg?"
output:
  flexdashboard::flex_dashboard:
    storyboard: yes
    social: menu
    source: embed
    css: style.css
---

```{r setup, include=FALSE}
library(sf)
library(plotly)
library(ggplot2)
library(leaflet)
library(mapview)
library(htmltools)
source("functions.R")
```


### How far is **KG Alpensiedlung** from **ÖJAB-Haus**? {data-commentary-width=400}

```{r}
dirfile_ojab <- "data/OJAB/Points.shp"
dirfile_kinde <- "data/kindergarden.shp.shp"
dirfile_drive_time <- "data/01_driving_time.geojson" 
dirfile_drive_distance <- "data/01_driving_distance.geojson" 
dirfile_walk_distance <- "data/01_walking_time.geojson"
map_01(dirfile_ojab, dirfile_kinde,
       dirfile_drive_time, dirfile_drive_distance,
       dirfile_walk_distance)
```

------------------------------------------------------------------------

<div class="floro">
**KG Alpensiedlung** is one of the most modern and, therefore, most popular kindergartens in the southern part of Salzburg. If we consider **ÖJAB-Haus** as our starting point, the minimum walking distance to **KG Alpensiedlung** (line blue) is about **5.21 km**, being necessary more than one hour to reach our destination. 

On the other hand, if we consider a car as a means of transport we can find two potential roads. The first one (black dotted line) reaches **KG Alpensiedlung** after 11.31 minutes (6.12 km), while the second one (red line) reaches it in 11.37 minutes (5.72 km).
</div>

### Closest glass waste containers to **ÖJAB-Haus** {data-commentary-width=400}

```{r}
dirfile_walk_distance <- "data/water_container.shp"
map_02(dirfile_ojab, dirfile_walk_distance)
```

------------------------------------------------------------------------
<div class="floro">

The three closest water containers to **ÖJAB-Haus Salzburg** are less than **1 km <sup> 2 </sup>** away (see purple lines). Reach to any of them would take less than 10 minutes walking.

</div>

### Optimizing waste glass collection in Salzburg - I. {data-commentary-width=400}

```{r}
map_04()
```

------------------------------------------------------------------------

<div class="floro">
Using three trucks, 3 routes were generated:

  - **Route # 1 (network):** With a total distance of 36 miles and 122 minutes of total travel.
  
  - **Route # 2 (orange):** With a total distance of 32 miles and 111 minutes of total travel.
  
  - **Route # 3 (blue):** With a total distance of 32 miles and 103 minutes of total travel.
</div>

### Optimizing waste glass collection in Salzburg - II. {data-commentary-width=400}

```{r}
ggviz <- wranglig_route_data()$ggviz
ggplotly(ggviz)
```

------------------------------------------------------------------------

<div class="floro">
Using three trucks, 3 routes were generated:

  - **Route # 1 (network):** With a total distance of 36 miles and 122 minutes of total travel.
  
  - **Route # 2 (orange):** With a total distance of 32 miles and 111 minutes of total travel.
  
  - **Route # 3 (blue):** With a total distance of 32 miles and 103 minutes of total travel.

We can see that the average glass waste collection time varies slightly in each route (approximately 1.8 min for each point). The extreme values presented by this box plot are related to the distance between **Siggerwiesen** and the first collection point.
</div>

### Analyzing different walking time distance. {data-commentary-width=400}

```{r echo=FALSE}
map_03()
```

------------------------------------------------------------------------

<div class="floro">
The side map show us the area of influence of the 4 most popular kindergardens in Salzburg: **AGG "English Play Corner"**, **AGG Vogelweiderstrasse**, **R.k. Pfarr-KG Dompfarre**, and 
**KG Alpensiedlung**.

Unlike the [horizontal distance assignment](https://csaybar.github.io/digitalearth/assigments/spatial_analisys/assigment_01/assigment_01.html) we considerate the walking time distance each for 4,8 and 10 minutes.

In contrast to the horizontal distance, the walking time distance has a more irregular shape, which is linked to the complexity of the streets. That is the reason why each kindergarten has a unique geometry.

</div>
